The Name of the Title Is Hope

### 2024-11-26 paper/paper.tex
Added data synthesis

\subsection{Methodology}

@@

% This research is implemented in Python Jupyter notebooks and is publicly available.

@@

Underneath the hood, the tool employs a Markov random field (MRF) and the select step corresponds to marking cliques in an MRF. By default, all $1$-way marginals are selected to preserve the quantity of each attribute element.

We can further preserve correlations by adding $n$-way marginals. For example, if we want to preserve the relationship between sex and race, we may add the clique containing sex and race.

@@

For the competition, Ryan McKenna further manually added certain cliques based on his investigation of the competition dataset.

For the select step, we followed the techniques used by . We further added edges according to a fraction of the upper bounds of each MI by calculating the Shannon entropies.

For the measure and generate step, we simply followed the examples provided in the tool's repository. We added Gaussian noise to the marginals. we spent half of the privacy budget $\epsilon = 1$ on all 1-way marginals and the other on the MRF cliques. And then we generate synthetic data of size similar to the original database. By \cite{mckenna2021winning}, this procedure satisfies $(\alpha,\frac{\alpha}{2 \sigma^2})$-RDP for all $\alpha \geq 1$.

\subsection{Fairness Checker}

We used the fairness checker from \cite{yuan2024ensuring}. We set the privileged predicate $\priv$ to male and the positive predicate $\pos$ to the positive prediction of each of the corresponding dataset.

@@

We extracted various models from Kaggle. They are finetuned to perform well on the original dataset. For one, a random forest model is finetuned by searching hyperparameters settings\cite{Ipbyrne2023}. For another, a logistic regression model is finetuned by performing principal component analysis\cite{Prashant1112023}.

>>>>

\section{Methodology}

@@

This research is implemented in Python Jupyter notebooks and is publicly available.

\subsection{Data Synthesis}

@@

Underneath the hood, the tool employs a Markov random field (MRF). The select step corresponds to marking cliques in an MRF, and the generate step corresponds to sampling from the fitted MRF.

By default, all $1$-way marginals are selected to preserve the quantity of each attribute element. We can further preserve correlations by adding $n$-way marginals. For example, if we want to preserve the relationship between sex and race, we may add the clique (sex,race).

@@

For the competition, Ryan McKenna further manually added certain cliques based on his investigation of the competition dataset. For example, he manually added the clique (sex,city,income). In addition, he would add some edges based on some heuristics tailored to that particular dataset.

We came up with an alternative heuristic for a general purpose workflow. Since MIs are bounded by the minimum of the pair's respective Shannon entropies, we add additional edges according to a fraction of this upper bounds.

For the measure step, we followed the examples provided in the tool's repository. Gaussian noises are added to the selected marginals. Half of the privacy budget are spent on all 1-way marginals and the other half on the selected cliques. These marginals are then fed to the tool to fit the MRF. By \cite{mckenna2021winning}, this procedure satisfies $(\alpha,\frac{\alpha}{2 \sigma^2})$-RDP for all $\alpha \geq 1$.

\subsection{Fairness Checking}

% We used the fairness checker from \cite{yuan2024ensuring}. We set the privileged predicate $\priv$ to male and the positive predicate $\pos$ to the positive prediction of each of the corresponding dataset.

@@

% We extracted various models from Kaggle. They are finetuned to perform well on the original dataset. For one, a random forest model is finetuned by searching hyperparameters settings\cite{Ipbyrne2023}. For another, a logistic regression model is finetuned by performing principal component analysis\cite{Prashant1112023}.
